Generating Simulated Data

### 2021-04-07 docs/SimData.Rmd
all libraries at top

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
library(here)
library(tidyverse)  
library(atlantisom)
library(ggthemes)

@@

library(FSA)
vb1 <- vbFuns()
# VBGF packages all take age and length pairs, reformat from length comp at agecl
# break into 3 chunks of time, "era" 48 years each more like our survey
# subsample after reformatting with uncount because we wouldn't have this many ages

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
library(here)
library(tidyverse)  
library(atlantisom)
library(ggthemes)
library(FSA)

@@

vb1 <- vbFuns()
# VBGF packages all take age and length pairs, reformat from length comp at agecl
# break into 3 chunks of time, "era" 48 years each more like our survey
# subsample after reformatting with uncount because we wouldn't have this many ages
